---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE, eval=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(tcam)
library(ggplot2) # for plotting

# current version
packageVersion("tcam")

```

Open a connection to the tCam:

```{r ex-01a-show, eval=FALSE}
con <- tcam_connect()
```

```{r ex-01a-hidden, echo=FALSE}
con <- tcam_connect("10.1.10.89")
```

Get the tCam status:

```{r ex-01b}
get_status(con)
```

Take a picture and plot it:

```{r ex-02}
img <- get_image(con)

ggplot(tidy_radiometric(img)) +
  geom_tile(
    aes(x, y, fill = value),
    color = NA
  ) +
  scale_fill_viridis_c(
    name = "°F",
    option = "magma"
  ) +
  coord_fixed() +
  labs(
    x = NULL, y = NULL
  ) +
  theme_minimal() +
  theme(
    axis.text.x.bottom = element_blank(),
    axis.text.y.left = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
```

Done, so we close the connection (kinda important)

```{r ex-99}
close(con)
```

## tcam Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
